Clustering: A pipeline to analyse time-course gene expression data

### 2019-02-19 scripts/03_clustering.Rmd
ENH Adding nicer colors to centroids

```{r echo=FALSE, results="hide"}
# Loading dependencies
library(devtools)
library(limma)
library(splines)
library(stats)
library(moanin)

# library(moanin)
```

@@

kmeans_clusters = moanin::splines_kmeans(
    y, meta, n_clusters=20,
    random_seed=42,
    degrees_of_freedom=df)

@@

```{r fig.height=8, fig.width=8}
moanin::plot_centroids(centroids, meta)
```

```{r results="hide", echo=FALSE}
# Save the clustering for the next step
write.table(kmeans_clusters$clusters,
	    ".results/clustering_labels.txt",
	    sep="\t")
```

>>>>

```{r echo=FALSE, results="hide"}
# Loading dependencies
library(devtools)
library(limma)
library(splines)
library(stats)
library(moanin)
source("utils.R")
# library(moanin)
```

@@

kmeans_clusters = moanin:::splines_kmeans(
    y, meta, n_clusters=20,
    random_seed=42,
    degrees_of_freedom=df)

@@

```{r fig.height=8, fig.width=8}
moanin:::plot_centroids(centroids, meta,
			colors=as.vector(unlist(ann_colors["Group"])))
```

```{r results="hide", echo=FALSE}
# Save the clustering for the next step
kmeans_labels = as.data.frame(kmeans_clusters$clusters)
row.names(kmeans_labels) = row.names(y)
write.table(kmeans_labels,
	    ".results/clustering_labels.txt",
	    sep="\t")
```
